Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-01-18 manuscript.tex
Add some more discussion about multiple shooting
Issue #4

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.
\Cref{fig:multiple shooting} shows a schematic representation of the multiple shooting procedure.

@@

		    \node[label=below:\(t_0\)] (t0) at (0,0) {};
		    \node[label=below:\(t_1\)] (t1) at (5,0) {};
		    \node[label=below:\(t_2\)] (t2) at (10,0) {};
		    \node[label=below:\(t_{n-1}\)] (t3) at (15,0) {};
		    \node[label=below:\(t_n\)] (tn) at (20,0) {};

		    % nodes for each subsegment
		    \node[label=left:\(\vecbf{x}_0\)] (x0) at (0,1) {\pgfuseplotmark{*}};

		    \node[label=right:\(\vecbf{x}_1^{-}\)] (x1minus) at (5,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_1^{+}\)] (x1plus) at (5,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_2^{-}\)] (x2minus) at (10,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_2^{+}\)] (x2plus) at (10,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_{n-1}^{-}\)] (x3minus) at (15,2) {\pgfuseplotmark{*}};
		    \node[label=left:\(\vecbf{x}_{n-1}^{+}\)] (x3plus) at (15,3) {\pgfuseplotmark{o}};

		    \node[label=right:\(\vecbf{x}_n\)] (xnminus) at (20,3) {\pgfuseplotmark{*}};
		    % draw axes
		    \draw [<->,thick] (tn.center) -- (t0.center) -- (x0m.center);

@@

		    % draw the subsegments
		    \draw [->] (x0.center) to [bend left=30] (x1minus.center);
		    \draw [->] (x1plus.center) to [bend left=30] (x2minus.center);
		    % dotted lines here
		    \draw[decorate sep={2mm}{10mm},fill] (x2plus.east) to [bend left=30] (x3minus.west);

@@

More detail on how the multiple shooting works
Explain the image
Additional interior constraints are used to ensure a continuous solution.
This has the benefit of decreasing the numerical sensitivity of the final states to changes in the initial conditions along each sub-arc.
% tpbvp is solved using a shooting method (fsolve in matlab)
% determine a design vector X of variables we need to determine
% define a constraint vector G(X) that we need to satisfy
% multiple shooting has interior points of continuity constraints
% sensitivity of terminal state is used to correct the initial condition (cite a book/paper)
% plot of multiple shooting ( stages)
\section{Numerical Example}\label{sec:simulation}
We present two numerical simulations in the Earth-Moon system to demonstrate the transfer procedure.
These simulations enable the spacecraft to depart from the natural dynamics through the use of low-thrust propulsion.
The reachability set on the \Poincare section allows for a straightforward method of determining transfer opportunities.

>>>>

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.

@@

		    \node[label=below:\(k_0\)] (t0) at (0,0) {};
		    \node[label=below:\(k_1\)] (t1) at (5,0) {};
		    \node[label=below:\(k_2\)] (t2) at (10,0) {};
		    \node[label=below:\(k_{n-1}\)] (t3) at (15,0) {};
		    \node[label=below:\(k_n\)] (tn) at (20,0) {};

		    % nodes for each subsegment
		    \node[label=left:\(\vecbf{x}_0\)] (x0) at (0,1) {\pgfuseplotmark{*}};
		    \node[label=below left:\(\vecbf{\lambda}_0\)] at (x0) {};

		    \node[label=right:\(\vecbf{x}_1^{-}\)] (x1minus) at (5,2) {\pgfuseplotmark{*}};
		    \node[label=below right:\(\vecbf{\lambda}_1^{-}\)] at (x1minus) {};

		    \node[label=above left:\(\vecbf{x}_1^{+}\)] (x1plus) at (5,3) {\pgfuseplotmark{o}};
		    \node[label=left:\(\vecbf{\lambda}_1^{+}\)] at (x1plus) {};

		    \node[label=right:\(\vecbf{x}_2^{-}\)] (x2minus) at (10,2) {\pgfuseplotmark{*}};
		    \node[label=below right:\(\vecbf{\lambda}_2^{-}\)] at (x2minus) {};

		    \node[label=above left:\(\vecbf{x}_2^{+}\)] (x2plus) at (10,3) {\pgfuseplotmark{o}};
		    \node[label=left:\(\vecbf{\lambda}_2^{+}\)] at (x2plus) {};

		    \node[label=right:\(\vecbf{x}_{n-1}^{-}\)] (x3minus) at (15,2) {\pgfuseplotmark{*}};
		    \node[label=below right:\(\vecbf{\lambda}_{n-1}^{-}\)] at (x3minus) {};

		    \node[label=above left:\(\vecbf{x}_{n-1}^{+}\)] (x3plus) at (15,3) {\pgfuseplotmark{o}};
		    \node[label=left:\(\vecbf{\lambda}_{n-1}^{+}\)] at (x3plus) {};

		    \node[label=right:\(\vecbf{x}_n\)] (xnminus) at (20,3) {\pgfuseplotmark{*}};
		    \node[label=below right:\(\vecbf{\lambda}_n\)] at (xnminus) {};
		    % draw axes
		    \draw [<->,thick] (tn.center) -- (t0.center) -- (x0m.center);

@@

		    % draw the subsegments
		    \draw [->] (x0.center) to [bend left=30] (x1minus.center);
		    \draw [->] (x1plus.center) to [bend left=30] (x2minus.center);
		    % dotted lines here
		    \draw[decorate sep={1mm}{5mm},fill] (x2plus.east) to [bend left=10] (x3minus.west);

@@

In~\cref{fig:multiple shooting} we show a schematic representation of the multiple shooting procedure.
We split the optimal control horizon into equal length subsegments such that the length of each segment is \( \frac{k}{n} \), where \( k, n \) are the total number of steps and number of stages, respectively.
Similarly, we divide the state and costate trajectories into \( n \) equal segments. 
To ensure continuity, additional interior constraints are incorporated as
\begin{subequations}
\begin{align}\label{eq:interior_constraints}
	\vecbf{x}_1^{-} - \vecbf{x}_1^{+} &= 0 , \\ 
	\vecbf{\lambda}_1^{-} - \vecbf{\lambda}_1^{+} &= 0 , \\
	\vecbf{x}_2^{-} - \vecbf{x}_2^{+} &= 0 , \\ 
	\vecbf{\lambda}_2^{-} - \vecbf{\lambda}_2^{+} &= 0 , \\
	&\vdots \\
	\vecbf{x}_{n-1}^{-} - \vecbf{x}_{n-1}^{+} &= 0 , \\ 
	\vecbf{\lambda}_{n-1}^{-} - \vecbf{\lambda}_{n-1}^{+} &= 0.
\end{align}
\end{subequations}
Using the multiple shooting method reduces the sensitivity of the terminal states, \( \vecbf{x}_i^{+}, \vecbf{\lambda}_i^{+}\), to variations of the initial states, \(\vecbf{x}_{i-1}^{-}, \vecbf{\lambda}_{i-1}^{-}\).
The constraints to be satisfied are defined by~\cref{eq:interior_constraints,eq:necc_cond} through selection of \( \vecbf{\lambda}_0, \vecbf{\beta}, \vecbf{x}_i^{+}, \text{ and } \vecbf{\lambda}_i^{+} \).

% tpbvp is solved using a shooting method (fsolve in matlab)
% determine a design vector X of variables we need to determine
% define a constraint vector G(X) that we need to satisfy
% multiple shooting has interior points of continuity constraints
% sensitivity of terminal state is used to correct the initial condition (cite a book/paper)
% plot of multiple shooting ( stages)
\section{Numerical Example}\label{sec:simulation}
We present two numerical simulations in the Earth-Moon system to demonstrate the transfer procedure.
These simulations enable the spacecraft to depart from the natural dynamics through the use of low-thrust propulsion.
The reachability set on the \Poincare section allows for a straightforward method of determining transfer opportunities.
